## Average Approximating on Continuous Information

Agregation process on discete information will be described here using temperature data. 5 minutes time interval will be used for curating the timestamps.

#### Loading Sample Data
```{r message=F,warning=F}
library(devtools)
source_url("https://raw.githubusercontent.com/OptiRTC/export-analysis/ZyuAFD-patch-1/Data/Loading%20Sample%20Data.R?token=AKLn5qtCQw2wdWyFj7-K_iBfF_SC7qI1ks5acIeYwA%3D%3D")
```

#### This code is a sample of aggregation of rain gauge data on Sample data. 

- The data quality is first checked of the duplicated time step for Temperature data

```{r Check data quality on duplicated steps,message=F,warning=F}

# Extract Rain information for analysis
Temp_dt=GoldaMeir_Dt %>% select(Time,Temp) 

Temp_dt %>% head(10)%>% kable

# Check duplicate time step

Temp_dt %>% 
    group_by(Time) %>% 
    tally %>% 
    filter(n>1) %>% 
    arrange(-n)
```


- Time steps are then rounded up to a time interval value of 5 minutes ( This string has to be among the built-in strings for "unit" parameter in [lubridate::round_date](https://github.com/tidyverse/lubridate/blob/master/R/round.r) function). In this case, [lubridate::floordate](https://github.com/tidyverse/lubridate/blob/master/R/round.r) is used since rain gauge data is a cumulative value aggregated down to its nearest round time point.
- Check the duplicated time interval and aggregate the rain data upon it

```{r Aggregation on rain data in specified time interval,message=F,warning=F}
Time_Intv= "5 mins" # constant of time interval

library(padr)
Temp_dt %>% 
        select(Time) %>% 
    # Get the range of date
        summarize(min(Time),max(Time)) %>% 
    gather() %>% 
    select(value) %>% 
    mutate(value=lubridate::round_date(value,Time_Intv)) %>% 
    # Get the complete time stamps
    pad(interval=Time_Intv) ->Time_cmplt


# Approximate Temperature to target time stamps by linear interpolation 
library(zoo)
Temp_dt_Cur=Time_cmplt %>% 
    mutate(Temp=na.approx(as.numeric(Temp_dt$Temp),x=Temp_dt$Time,xout=Time_cmplt$value,na.rm=F)) %>% 
    mutate(Temp=Temp* make_unit("degF")) %>% 
    rename(Time=value)
      
Temp_dt %>% arrange(Time) %>% head(15)
Temp_dt_Cur %>% arrange(Time) %>% head(15)


```

Since the timestamps have already curated to complete series (no gaps), there is no need to check the data gaps in the result dataset.





